### 2014-04-02 Docs/getting_started/getting_started.tex
start of an index just for runtime parameters

Parameters that set the maximum time for the simulation to run
include:
\begin{itemize}
\item {\tt stop\_time} is the maximum simulation time, in seconds,
      to evolve the system for.

\item {\tt max\_step} is the maximum number of steps to take.
\end{itemize}

\noindent Parameters affecting the size of the timestep include:
\begin{itemize}
\item {\tt cflfac} is a multiplicative factor ({\tt $\le 1$}) 
      applied to the advective CFL timestep

\item {\tt init\_shrink} is the factor ({\tt $\le 1$}) by which to reduce 
      the initial timestep from the estimated first timestep.
\end{itemize}

@@

\item {\tt restart} tells \maestro\ to restart from a checkpoint.  The
      value of this parameter should be the file number to restart from.
      For example, to restart from the checkpoint file {\tt chk00010},
      you would set {\tt restart = 10}.

\item {\tt plot\_int} is the number of steps to take between
  outputting a plotfile

\item {\tt plot\_deltat} is the simulation time to evolve between
  outputting a plotfile.  Note: to output only based on simulation
  time, set {\tt plot\_int = -1}.

\item {\tt check\_int} is the number of steps to take between
  outputting a checkpoint.

@@

\item {\tt max\_levs } is the maximum number of grid levels in the AMR
  hierarchy to use.  {\tt max\_levs = 1} indicates running with only a
  single level spanning the whole domain.

\item {\tt n\_cellx }, {\tt n\_celly }, {\tt n\_cellz } the size of
  base level in terms of number of cells, in the $x$, $y$, and $z$
  coordinate directions.

\item {\tt max\_grid\_size } the maximum extend of a grid, in any
  coordinate direction, as measured in terms of number of cells.

  For multilevel problems, the parameter {\tt max\_grid\_size\_1}
  controls the maximum extent on level 1 (the base grid), {\tt
    max\_grid\_size\_2} controls the maximum extent on level 2, and
  {\tt max\_grid\_size\_3} controls the maximum extent on levels 3 and
  higher.

\item {\tt prob\_lo\_x }, {\tt prob\_lo\_y }, {\tt prob\_lo\_z } is
  the physical coordinate of the lower extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

\item {\tt prob\_hi\_x }, {\tt prob\_hi\_y }, {\tt prob\_hi\_z } is
  the physical coordinate of the upper extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

@@

   \item {\tt bcx\_lo }, {\tt bcy\_lo }, {\tt bcz\_lo }, {\tt bcx\_hi
      }, {\tt bcy\_hi }, {\tt bcz\_hi } are the boundary condition
      types at the lower (`{\tt lo}') and upper (`{\tt hi}') domain
      boundaries in the $x$, $y$, and $z$ coordinate directions.  The
      different types are set via integer flags listed in
      table~\ref{gs:table:bcflags}.

@@

   \item {\tt xlo\_boundary\_type}, {\tt ylo\_boundary\_type}, {\tt
   zlo\_boundary\_type}, {\tt xhi\_boundary\_type}, {\tt
   yhi\_boundary\_type}, {\tt zhi\_boundary\_type} are the boundary
   condition types at the lower and upper domain boundaries in 
   the $x$, $y$, and $z$ coordinate directions.   The boundary
   type is set by providing a string name---valid values are listed
   in table~\ref{gs:table:bcstrings}

>>>>

Parameters that set the maximum time for the simulation to run
include:
\begin{itemize}
\item \runparam{stop\_time} is the maximum simulation time, in seconds,
      to evolve the system for.

\item \runparam{max\_step} is the maximum number of steps to take.
\end{itemize}

\noindent Parameters affecting the size of the timestep include:
\begin{itemize}
\item \runparam{cflfac} is a multiplicative factor ({\tt $\le 1$}) 
      applied to the advective CFL timestep

\item \runparam{init\_shrink} is the factor ({\tt $\le 1$}) by which to reduce 
      the initial timestep from the estimated first timestep.
\end{itemize}

@@

\item \runparam{restart} tells \maestro\ to restart from a checkpoint.  The
      value of this parameter should be the file number to restart from.
      For example, to restart from the checkpoint file {\tt chk00010},
      you would set {\tt restart = 10}.

\item \runparam{plot\_int} is the number of steps to take between
  outputting a plotfile

\item \runparam{plot\_deltat} is the simulation time to evolve between
  outputting a plotfile.  Note: to output only based on simulation
  time, set {\tt plot\_int = -1}.

\item \runparam{check\_int} is the number of steps to take between
  outputting a checkpoint.

@@

\item \runparam{max\_levs} is the maximum number of grid levels in the AMR
  hierarchy to use.  {\tt max\_levs = 1} indicates running with only a
  single level spanning the whole domain.

\item \runparam{n\_cellx}, \runparam{n\_celly}, \runparam{n\_cellz} the size of
  base level in terms of number of cells, in the $x$, $y$, and $z$
  coordinate directions.

\item \runparam{max\_grid\_size} the maximum extend of a grid, in any
  coordinate direction, as measured in terms of number of cells.

  For multilevel problems, the parameter \runparam{max\_grid\_size\_1}
  controls the maximum extent on level 1 (the base
  grid), \runparam{max\_grid\_size\_2} controls the maximum extent on
  level 2, and \runparam{max\_grid\_size\_3} controls the maximum extent on
  levels 3 and higher.

\item \runparam{prob\_lo\_x}, \runparam{prob\_lo\_y}, \runparam{prob\_lo\_z} is
  the physical coordinate of the lower extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

\item \runparam{prob\_hi\_x}, \runparam{prob\_hi\_y}, \runparam{prob\_hi\_z} is
  the physical coordinate of the upper extent of the domain boundary
  in the $x$, $y$, and $z$ coordinate directions.

@@

   \item \runparam{bcx\_lo}, \runparam{bcy\_lo}, \runparam{bcz\_lo
      }, \runparam{bcx\_hi}, \runparam{bcy\_hi}, \runparam{bcz\_hi} are the
      boundary condition types at the lower (`{\tt lo}') and upper
      (`{\tt hi}') domain boundaries in the $x$, $y$, and $z$
      coordinate directions.  The different types are set via integer
      flags listed in table~\ref{gs:table:bcflags}.

@@

   \item \runparam{xlo\_boundary\_type}, \runparam{ylo\_boundary\_type}, \runparam{zlo\_boundary\_type}, \runparam{xhi\_boundary\_type}, \runparam{yhi\_boundary\_type}, \runparam{zhi\_boundary\_type}
   are the boundary condition types at the lower and upper domain
   boundaries in the $x$, $y$, and $z$ coordinate directions.  The
   boundary type is set by providing a string name---valid values are
   listed in table~\ref{gs:table:bcstrings}
